Modal Abstractions for Virtualizing Memory Addresses

### 2023-04-14 examples.tex
+

@@

$\specline{\exists \texttt{ fpaddr} \ldotp \ulcorner \texttt{aligned fpaddr} \urcorner \ast \texttt{rax}\mapsto_{\textsf{r}} \texttt{fpaddr} \ast \texttt{fpaddr} \mapsto_{\textsf{a}} (\texttt{wzero 64})  \ulcorner \texttt{entry\_present fpaddr}\urcorner}_{\rtv}$

@@

$\specline{\exists \texttt{ fpaddr} \ldotp \ulcorner \texttt{aligned fpaddr} \urcorner \ast \texttt{rax}\mapsto_{r} \texttt{fpaddr} \ast \texttt{fpaddr} \mapsto_{a} (\texttt{wzero 64})  \ulcorner \texttt{entry\_present fpaddr}\urcorner}_{\rtv}$

@@

$\specline{\textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}(\vaddr,\entryf,\entrytr,\entrytw,\paddr) \ast \ulcorner \theta \;!!\;\vaddr = \texttt{None}\urcorner \; \ast}_{\rtv}$
$\specline{\ulcorner \texttt{aligned fpaddr} \urcorner \ast \texttt{rax}\mapsto_{\textsf{r}} \texttt{fpaddr} \ast \texttt{fpaddr} \mapsto_{\textsf{a}} (\texttt{wzero 64}) }_{\rtv}$

@@

The crux point in the proof is updating the virtual L1 address (\textsf{pte\_addr}) to show the fresly allocated page address (\textsf{fpaddr}) in Line 22 to obtain
\[\texttt{pte\_addr} \mapsto_{\texttt{vpte}}  \; \paddr\; \textsf{fpaddr}  \qquad\qquad (\textsf{by Rule} \TirNameStyle{WriteToVirtMemFromReg})\]

by Rule \TirNameStyle{WriteToVirtMemFromReg} which allows proving the fact that virtual address updates without exposing its internal physical page-table memory accesses (Specification Line 26). 
Consequently, right at this point in the proof, when we unfold the $\texttt{pte\_addr} \mapsto_{\texttt{vpte}}  \; \paddr\; \textsf{fpaddr})$ we will be able obtain a full ownerhsip on the L1 table physical pointsto $\paddr \mapsto_{\mathsf{p}} \textsf{fpaddr}$ . Then, we can split this full-ownership into to obtain a fractional ownership (q4) on it ($\paddr \mapsto_{\mathsf{p}} \{q4\} \;\textsf{fpaddr}$). Finally, we can connect this fragmental ownership with the L4-L2 physical table pointstos (Specification Lines 24 and 25) to obtain the complete physical table-walk assertion (L4\_L1\_PointsTo(maddr l4e l3e l2e pa)) in Line 30.

>>>>

$\specline{  \nfpointsto{\mask\vaddr\maskthree\entryf}{\mask\vaddr\maskthreeoff\entryf}\entrytr\qtwo\naddr \ast \nfpointsto{\mask\vaddr\masktwo\entrytr}{\mask\vaddr\masktwooff\entrytr}\paddr\qthree\entryo \;\ast}_{\rtv}$

@@

$\specline{\exists \texttt{ fpaddr} \ldotp \ulcorner \texttt{aligned fpaddr} \urcorner \ast \texttt{rax}\mapsto_{\textsf{r}} \texttt{fpaddr} \ast \texttt{fpaddr} \mapsto_{\textsf{p}} (\texttt{wzero 64})  \ulcorner \texttt{entry\_present fpaddr}\urcorner}_{\rtv}$

@@

$\specline{\exists \texttt{ fpaddr} \ldotp \ulcorner \texttt{aligned fpaddr} \urcorner \ast \texttt{rax}\mapsto_{r} \texttt{fpaddr} \ast \texttt{fpaddr} \mapsto_{p} (\texttt{wzero 64})  \ulcorner \texttt{entry\_present fpaddr}\urcorner}_{\rtv}$

@@

$\specline{\textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}(\vaddr,\entryf,\entrytr,\entrytw,\fpaddr) \ast \ulcorner \theta \;!!\;\vaddr = \texttt{None}\urcorner \; \ast}_{\rtv}$
$\specline{\ulcorner \texttt{aligned fpaddr} \urcorner \ast \texttt{rax}\mapsto_{\textsf{r}} \texttt{fpaddr} \ast \texttt{fpaddr} \mapsto_{\textsf{p}} (\texttt{wzero 64}) }_{\rtv}$

@@

The crux point in the proof is updating L1 table through a virtual address (\textsf{pte\_addr}) through making a known physical address, in our example L1 table entry address ($\textsf{addr\_L1}(\textsf{va, l1e})$), to show the fresly allocated page address (\textsf{fpaddr}) in Line 22 to obtain
\[\texttt{pte\_addr} \mapsto_{\texttt{vpte}}  \; \paddr\; \textsf{fpaddr}  \qquad\qquad (\textsf{by Rule} \TirNameStyle{WriteToVirtMemFromReg})\]
by Rule \TirNameStyle{WriteToVirtMemFromReg} (Specification Line 26). 
Consequently, right at this point in the proof, when we unfold the $\texttt{pte\_addr} \mapsto_{\texttt{vpte}}  \; \paddr\; \textsf{fpaddr})$ we will be able obtain a full ownerhsip on the L1 table physical pointsto $\paddr \mapsto_{\mathsf{p}} \textsf{fpaddr}$ . Then, we can first discard the allocated virtual-address pointsto assertion (i.e. dropping \textsf{pte\_addr}), and split the full-ownership of physical-page pointsto ($\textsf{fpaddr}\mapsto_{\textsf{p}} \;\textsf{wzero 64}$) to obtain a fractional ownership (q4) on it. Since we know $\texttt{addr\_L1 }(\vaddr, \entryo) \mapsto_{\mathsf{p}} \{q4\} \;\textsf{fpaddr}$) from $\mapsto_{\textsf{vpte}}$, after the drop of virtual-pointsto, we still can connect L4-L2 pointsto assertions (in Specification Lines 24 and 25) with newly allocated $\texttt{fpaddr} \mapsto_{a} (\texttt{wzero 64})$ to obtain the complete physical table-walk assertion (L4\_L1\_PointsTo(maddr l4e l3e l2e fpaddr)) in Line 30.
